Distributional Trees and Forests

### 2017-06-23 pkg/disttree/inst/useR2017/slides.Rnw
added comments on the 3 main functions 'distfit', 'disttree' and 'distforest'
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1486 255f4249-2263-4417-b1ea-8498779e27a7
capitalized first word and added point in slide 'Software'
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1488 255f4249-2263-4417-b1ea-8498779e27a7
edits in software and references
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1489 255f4249-2263-4417-b1ea-8498779e27a7

  if(!(any(dt.par, df.par, g.par, all.par, all.var))){
    par(mar=c(5.1,4.1,4.1,3.1))
    plot(y = sp$y, x = sp$x, type = "p", col="grey", main = "True parameters", xaxt='n', yaxt='n', xlab = "", ylab = "")
    lines(x = sp$x, y = sp$true.mu, type = "l", col = 'black')
    polygon(c(sp$x, rev(sp$x)), c(sp$true.mu + sp$true.sigma, rev(sp$true.mu - sp$true.sigma)),
  col = transpgrey, border = "transparent")
    #lines(x = sp$x, y = sp$true.mu + sp$true.sigma, type = "l", lty = 1, col = 'grey')
    #lines(x = sp$x, y = sp$true.mu - sp$true.sigma, type = "l", lty = 1, col = 'grey')
    legend('topleft', c(TeX('$\\mu$'), TeX('$\\mu \\pm \\sigma$')), 
           col = c('black',transpgrey, transpgrey), lty = c(1,1,1), bty = 'n')
  }

@@

\begin{frame}
\frametitle{Software}
\vspace{0.4cm}
R-package \pkg{disttree} available on R-Forge:\\
\vspace{0.2cm}
\url{https://R-Forge.R-project.org/projects/partykit/}\\
\vspace{1cm}
Main functions:
\vspace{0.2cm}
\begin{itemize}
\item \code{distfit()}: distributional fit, no covariates, gamlss.family, ML
\item \code{disttree()}: tree algorithm \code{ctree} or \code{mob}, \\
\hspace{2.18cm} covariates as splitting variables
\item \code{distforest()}: ensemble of trees,\\
\hspace{2.58cm} covariates as splitting variables
\end{itemize}
\end{frame}

@@

Hothorn T, Hornik K, Zeileis A (2006).\\
 \dquote{Unbiased Recursive Partitioning: A Conditional Inference Framework.}\\
 \textit{Journal of Computational and Graphical Statistics},
 \textbf{15}(3), 651--674.\\
 %URL~\url{http://    }

\bigskip

Zeileis A, Hothorn T, Hornik K (2008).\\
 \dquote{Model-Based Recursive Partitioning.}\\
  \textit{Journal of Computational and Graphical Statistics},
  \textbf{17}(2), 492--514.\\
  %\doi{10.1198/106186008X319331}

\bigskip

Hothorn T, Zeileis A (2015).\\
 \dquote{Partykit: A Modular Toolkit for Recursive Partytioning in R.}\\
 \textit{Journal of Machine Learning Research},
 \textbf{16}, 3905--3909.\\

\bigskip

Stasinopoulos DM, Rigby RA, et al. (2007).\\
  \dquote{Generalized Additive Models for Location Scale and Shape (GAMLSS) in R.}\\
  \textit{Journal of Statistical Software}, 
  \textbf{23}(7), 1--46.\\

\bigskip

Seibold H, Zeileis A, Hothorn T (2016).\\
  \dquote{Model-Based Recursive Partitioning for Subgroup Analyses.}\\
  \textit{The international journal of biostatistics}, 
  \textbf{12}(1), 45--63.\\

>>>>

  if(!(any(dt.par, df.par, g.par, all.par, all.var))){
    par(mar=c(5.1,4.1,4.1,3.1))
    plot(y = sp$y, x = sp$x, type = "p", col="grey", main = "True parameters", xaxt='n', yaxt='n', xlab = "", ylab = "")
    lines(x = sp$x, y = sp$true.mu, type = "l", col = 'black')
    polygon(c(sp$x, rev(sp$x)), c(sp$true.mu + sp$true.sigma, rev(sp$true.mu - sp$true.sigma)),
  col = transpgrey, border = "transparent")
    #lines(x = sp$x, y = sp$true.mu + sp$true.sigma, type = "l", lty = 1, col = 'grey')
    #lines(x = sp$x, y = sp$true.mu - sp$true.sigma, type = "l", lty = 1, col = 'grey')
    legend('topleft', expression(mu %+-% sigma), bty = 'n')
  }

@@

\begin{frame}
\frametitle{Software}
\vspace{0.4cm}
\textbf{Package:} \emph{disttree} available on R-Forge at\\

\url{https://R-Forge.R-project.org/projects/partykit/}\\

\bigskip
\bigskip

\textbf{Main functions:}

\begin{tabular}{ll}
\code{distfit}    & Distributional fits (ML, \code{gamlss.family} or custom \code{list}).\\
                  & No covariates. \\
\code{disttree}   & Distributional trees (\code{ctree}/\code{mob} + \code{distfit}).\\
                  & Covariates as partitioning variables. \\
\code{distforest} & Distributional forests (ensemble of \code{disttree}s).\\
                  & Covariates as partitioning variables.
\end{tabular}

@@

Hothorn T, Hornik K, Zeileis A (2006).
 \dquote{Unbiased Recursive Partitioning: A Conditional Inference Framework.}
 \textit{Journal of Computational and Graphical Statistics},
 \textbf{15}(3), 651--674.
 \doi{10.1198/106186006X133933}

Zeileis A, Hothorn T, Hornik K (2008).
 \dquote{Model-Based Recursive Partitioning.}
  \textit{Journal of Computational and Graphical Statistics},
  \textbf{17}(2), 492--514.
  \doi{10.1198/106186008X319331}

Hothorn T, Zeileis A (2015).
 \dquote{partykit: A Modular Toolkit for Recursive Partytioning in R.}
 \textit{Journal of Machine Learning Research},
 \textbf{16}, 3905--3909.
 \url{http://www.jmlr.org/papers/v16/hothorn15a.html}

Stasinopoulos DM, Rigby RA (2007).
  \dquote{Generalized Additive Models for Location Scale and Shape (GAMLSS) in R.}
  \textit{Journal of Statistical Software}, 
  \textbf{23}(7), 1--46.
  \doi{10.18637/jss.v023.i07}

Seibold H, Zeileis A, Hothorn T (2017).
  \dquote{Individual Treatment Effect Prediction for Amyotrophic Lateral Sclerosis Patients.}
  \textit{Statistical Methods in Medical Research}, 
  \textbf{12}(1), 45--63.
  \doi{10.1177/0962280217693034}

Hothorn T, Zeileis A (2017).
  \dquote{Transformation Forests.}
  \emph{arXiv 1701.02110}, arXiv.org E-Print Archive.
  \url{http://arxiv.org/abs/1701.02110}
